### 2023-02-22 paper.tex
updated VR

    \subsection{VR}

        (p2)

@@

\section{Appendix}
    % \begin{figure}[htbp!]
    %     \centering
    %     \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
    %     \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
    %     \label{fig}
    % \end{figure}

>>>>

    \subsection{VR}
        Another new method of robot programming attempts to combine the advantages of online and offline concepts. The idea is to use Virtual Reality to define needed motion sequences offline via simulation without any effort for the programmer. Therefore "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} For this purpose the programmer uses a VR headset which simulates a real environment and VR controllers to move freely within this simulation and to define the needed motion sequences for the robot. \cite[627]{p2}
        However the simulation is not suitable for small changes in the motion path, which is why Online-Programming is still be needed. It allows a fine-tuning directly in the targeted manufacturing process. If further changes or updates are required, the programme can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process. \cite[625]{p2}

@@

\section{Appendix}
    \begin{figure}[htbp!]
        \centering
        \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
        \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
        \label{fig}
    \end{figure}
